Stabilization-Free Virtual Element Methods

### 2023-03-12 reports/response.tex

%We thank the Referee for the valuable comments that helped us to improve the manuscript. In
%the revised version of the manuscript, all non-minor modifications are highlighted in red colour.
%Below, we address the points raised in the report.

\vskip0.5cm
\section{Response to Reviewer 1}
\begin{enumerate}[1.]

\item \textsf{The English presentation is unfortunately very dodgy and should be revised before any type of resubmission.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
We try our best to proofread the manuscript carefully.

@@

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
Thanks for this suggestion. We have removed the proof of Theorem 5.3.
We combine Section 5.2 and Section 5.3 in the revised manuscript.

\medskip

\item \textsf{In the numerical section, I agree that it is important to check the rate of convergence of the method.
However, the convergence does not automatically guarantee the invertibility of the local stiffness matrices, as imposing the Dirichlet boundary conditions may have a “stabilizing effect”. So, you should investigate the number of zero eigenvalues of the local stiffness matrix.\\
For instance, pick three different hexagonal elements with a fixed degree of accuracy, e.g., k = 3: the first being a regular hexagon; the second being a quasi-regular hexagon (small perturbation of the previous element); the third being a square with an edge containing two hanging nodes. Check whether the stiffness matrix always has only one zero eigenvalue, i.e., the method is indeed stabilization free.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
For the convenience of narration, we abbreviate the standard conforming virtual emelemt
method, the standard non-conforming virtual emelemt method, 
the stabilization-free conforming virtual element method,
and the stabilization-free non-conforming virtual element method as CVEM, NCVEM, SFCVEM, and SFNCVEM, respectively. 
We implement all the experiments on a PC with AMD Ryzen
5 3500U CPU and 64-bit Ubuntu 22.04 operating system.

We construct three different hexagons shown in Fig. \ref{fig:hexagon}, and calculate the eigenvalues of local stiffness matrices with $k=3$ for four virtual element methods. Our numerical results show that, on each different hexagon, both SFNCVEM and SFCVEM have only one zero eigenvalue. In Tables \ref{tab:comparison0}-\ref{tab:comparison2}, we also present the minimum non-zero eigenvalue, the maximum eigenvalue and the condition number for the local stiffness matrix on different hexagons in Fig. \ref{fig:hexagon}, by which we can see that these quantities are comparable for four virtual element methods.
\begin{figure}[htbp]
\subfigure[Regular hexagon.]{
\begin{minipage}[t]{0.3\linewidth}
\centering
\includegraphics*[width=1in]{../figures/hexagon0.pdf}
\end{minipage}}%% 
\;\;% \quad
\subfigure[Quasi-regular hexagon generated by regular
    hexagon with a small perturbation.]
{\begin{minipage}[t]{0.3\linewidth}
\centering
\includegraphics*[width=1in]{../figures/hexagon1.pdf}
\end{minipage}}
\;\;% \quad
\subfigure[Square with two hanging nodes.]
{\begin{minipage}[t]{0.35\linewidth}
\centering
\includegraphics*[width=0.9in]{../figures/hexagon2.pdf}
\end{minipage}}
\caption{The regular hexagon(Left), the quasi-regular hexagon generated by regular
    hexagon with a small perturbation (Middle), 
and the square with two hanging nodes (Right).}
\label{fig:hexagon}
\end{figure}
\begin{table}[htbp]
\centering
\caption{Comparison of eigenvalues and condition numbers on the regular hexagon.}
\label{tab:comparison0}
\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
\hline
\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
eigenvalue} & \textbf{Condition number} \\ \hline
NCVEM & 975.5693189 & 0.309674737 & 3150.303211 \\ \hline
CVEM & 1012.488116 & 0.297206358 & 3406.683909 \\ \hline
SFNCVEM & 992.5956147 & 0.318932029 & 3112.248147 \\ \hline
SFCVEM & 1011.173331 & 0.298509692 & 3387.405362 \\
\hline
\end{tabular}
\end{table}
\begin{table}[htbp]
\centering
\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
\label{tab:comparison1}
\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
\hline
\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
eigenvalue} & \textbf{Condition number} \\ \hline
NCVEM   & 935.2883848 & 0.279027715 & 3351.955143 \\ \hline
CVEM    & 1014.672395 & 0.257370621 & 3942.456177 \\ \hline
SFNCVEM & 997.4831245 & 0.282126359 & 3535.589964 \\ \hline
SFCVEM  & 1047.876056 & 0.258970708 &
4046.311124 \\
\hline
\end{tabular}
\end{table}
\begin{table}[htbp]
\centering
\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
\label{tab:comparison2}
\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
\hline
\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
eigenvalue} & \textbf{Condition number} \\ \hline
 NCVEM   & 941.8571938&	0.21069027	&4470.340249 \\ \hline
 CVEM    & 1046.755495&	0.200435123	&5222.4155 \\ \hline
 SFNCVEM & 986.5963357&	0.212761106	&4637.108513 \\ \hline
 SFCVEM  & 1061.651989&	0.202074633	&5253.761808 \\
\hline
\end{tabular}
\end{table}

@@

\medskip

\item \textsf{My feeling is that the proposed stabilization-free approach is much more expensive than the standard one. Thus, you should check the assembling time of the stabilization-free and standard VEMs, on: ($i$) a (reasonably large) sequence of meshes; ($ii$) fixing a mesh, increasing the degree of accuracy, e.g., up to $k = 10$.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
The only difference between the standard VEMs and the stabilization-free VEMs is the
stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
four different VEMs in detail by varying the degree $k$ and the mesh size $h$
respectively. We use the mesh in Fig.~\ref{fig:mesh} for this experiment.
\begin{figure}[htbp]
\centering
\includegraphics*[width=4.7cm]{../figures/convex.pdf}
\caption{Convex polygon mesh.}
\label{fig:mesh}
\end{figure}
The results presented in Tables
\ref{tab:ptime} and \ref{tab:ttime} show that NCVEM, CVEM and SFNCVEM have similar assembling time. 
However, SFCVEM requires more time due to the projection onto the one-order higher polynomial space.
\begin{table}[htbp]
\caption{Time consumed in assembling stiffness matrix of four VEMs with
 $h=0.2$ and different $k$.}
\label{tab:ptime}
\centering
\begin{tabular}{c|cccc}
\hline
$k$ & 2 & 4 & 8 & 10 \\
\hline
SFCVEM & 0.053684235 & 0.144996881 & 1.468627453 & 2.603836536 \\
SFNCVEM & 0.022516727 & 0.065697193 & 0.806378841 & 1.554260015 \\
CVEM & 0.021185875 & 0.059809923 & 0.600241184 & 1.160929918 \\
NCVEM & 0.0213027 & 0.061014891 & 0.596506596 & 1.129639149 \\
\hline
\end{tabular}
\end{table}
\begin{table}[htbp]
\caption{Time consumed in assembling stiffness matrix of four VEMs with $k = 5$ and different $h$.}
\label{tab:ttime}
\centering
\begin{tabular}{c|cccc}
\hline
$h$ &    1	& 0.25 & 0.0625 & 0.03125\\
\hline
SFCVEM & 0.039689541 & 0.199015379	& 1.74412179	& 4.75462532\\
SFNCVEM & 0.018287182 & 0.100006819	& 0.81251812	& 2.465409517\\
CVEM & 0.018686771 & 0.087426662	& 0.781031132	& 1.983617783\\
NCVEM & 0.018309593 & 0.096345425	& 0.767129898	& 2.159288645\\
\hline
\end{tabular}
\end{table}

@@

\medskip

\item \textsf{Along the same avenue, you should also compare the condition number of the global matrices obtained with the two approaches in the two situations ($i$) and ($ii$) above. Furthermore, you may also wish to consider sequences of meshes with “collapsing elements” (refine a mesh and change the aspect ratio), and check the condition numbers again. As a suggestion, since the condition number should be computed scaling the diagonal of the matrix, you can empirically check such conditioning by testing the two approaches on a patch test. The conditioning can be estimated checking the growth of the error for the patch test.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
\begin{figure}[htbp]
\centering
\subfigure{\includegraphics[width=1in]{../figures/hexagon0.pdf}}
    % \caption{Type I:5 tetrahedra}
%%
\subfigure{\includegraphics[width=1in]{../figures/hexagon3.pdf}}
     %\caption{Type II: 24 tetrahedra}
%%
\subfigure{\includegraphics[width=1in]{../figures/hexagon4.pdf}}
     %\caption{Trirectangular tetrahedron}
%%
\caption{The hexagons $H_0, H_1, H_2$.}
  \label{fig:collapsehexagon} %% label for entire figure
\end{figure} 
We design two experiments to check the condition number of the stiffness
matrices of the four VEMs.

Firstly, we refer to the ``collapsing polygons'' experiment in
\cite{Mascotto2018} and consider a sequence of hexagons
$\{H_i\}_{i=0}^{\infty}$, where the vertices of $H_i$ are given by
$A_i = (1, 0)$, $B_i = (0.5, a_i)$, $C_i = (-0.5, a)$, $D_i=(-1, 0)$, 
$E_i = (-0.5, -a_i)$, and $F_i = (0.5, -a_i)$,
where $a_i = \frac{\sqrt{3}}{2^{i+1}}$. The hexagons $H_0$, $H_1$ and $H_2$ are drawn
in Fig.~\ref{fig:collapsehexagon}. 
% We construct the virtual element space on $H_i$ and calculate the condition number
% of the stiffness matrix of four methods. 
As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber}, the condition numbers of stiffness
matrices of the stabilization-free methods are smaller than those of the standard methods when $i$ is large.

\begin{figure}[htbp]
\subfigure[$k = 8$]{
\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics*[width=2in]{../figures/collapsing_condition_number_8.pdf}
\end{minipage}}%% 
\quad \quad
\subfigure[$k = 10$]
{\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics*[width=2in]{../figures/collapsing_condition_number_10.pdf}
\end{minipage}}
\caption{The condition number of stiffness matrix of four VEMs on
$\{H_i\}_{i=0}^{12}$.}
\label{fig:collapsehexagon_conditionnumber}
\end{figure}

% \begin{figure}[htbp]
% \centering
% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_8.pdf}}
% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_10.pdf}}
% \caption{The condition number of stiffness matrix of four VEMs on
% $\{H_i\}_{i=0}^{12}$, Left : $k = 8$, Right : $k = 10$.}
%   \label{fig:collapsehexagon_conditionnumber0} %% label for entire figure
% \end{figure}

Secondly, we do the patch test for the Laplace equation, i.e. problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 0$ and $f=0$, but the Dirichlet boundary condition is nonhomogeneous. Take the exact solution $u=1+x+y$. %We adopt meshes in Fig. \ref{fig:polymesh}.
% $$
% \left\{\begin{aligned}
% -\Delta u & = 0 \quad x \in \Omega\\
% u & = g \quad x \in \partial \Omega
% \end{aligned}\right.
% $$
% where $\Omega = (0, 1)^2, \ u = g = 1+x+y$. 
Let $h_x$ and $h_y$ be mesh size in the $x$-direction and
$y$-direction respectively.
We examine the behavior of error $\|u - u_h\|_0$ of the four VEMs in the
following three cases:
\begin{enumerate}[(1)]
\item Mesh in Fig.~\ref{fig:mesh}: Fix $h_x=h_y=0.2$ but vary $k= 1, 2, \ldots, 10$;
\item Mesh in Fig.~\ref{fig:mesh}: Fix $k=3$ but vary $h_x=h_y=2^{-i}$ for $i=1,\ldots, 5$;
\item Mesh in Fig.~\ref{fig:polymesh}: Fix $k=3$ and $h_x=0.2$, but vary $h_y=2^{-i}$ for $i=1,\ldots, 8$.
\end{enumerate}
\begin{figure}[htbp]
\centering
% \subfigure{\includegraphics[width=2in]{./figures/poly_mesh.pdf}}
\subfigure{\includegraphics[width=2in]{../figures/mesh_hy.pdf}}
\caption{The mesh of domain $(0, 1)\times(0, 1)$ with
$h_x=0.2, h_y = 0.03125$.}
% \caption{The meshes of domain $(0, 1)\times(0, 1)$. Left: $h = 0.1$. Right:
% $h_x=0.2, h_y = 0.03125$.}
  \label{fig:polymesh} %% label for entire figure
\end{figure}
The errors of four methods shown in Fig. \ref{fig:patchtest} are similar. 
Since the error in the patch test
grows as the condition number of the stiffness matrix grows, 
the condition numbers of the stiffness matrix obtained by
four methods are similar.
\begin{figure}[htbp]
\centering
\subfigure{\includegraphics[width=1.7in]{../figures/patch_test_p.pdf}}
%%
\subfigure{\includegraphics[width=1.7in]{../figures/patch_test_h.pdf}}
%%
\subfigure{\includegraphics[width=1.7in]{../figures/patch_test_hy.pdf}}
  \label{fig:patchtest} %% label for entire figure
\caption{The $L^2$ error of patch test.}
\end{figure}

@@

The discrete bilinear form in this paper is defined as 
\[
a_h(u_h, v_h):=(Q_{h,k-1}^{\div}\nabla_h u_h, Q_{h,k-1}^{\div}\nabla_h v_h)+\alpha(Q_hu_h, Q_hv_h).
\]
The discrete Poincar\'e inequality established in \cite{Brenner2003} works for the virtual element space $V_h$
\[
\|v_h\|_0\lesssim |v_h|_{1,h}\quad\forall~v_h\in V_h.
\]
This means that $|\cdot|_{1,h}$ is indeed a norm for space $V_h$. Hence, to show the coercivity of the discrete bilinear form $a_h(\cdot, \cdot)$, it suffices to prove
\begin{equation}\label{eq:11}    
|v_h|_{1,h}^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
\end{equation}
The coercivity \eqref{eq:11} is (4.19) for the nonconforming virtual element method, and~(5.8) for the conforming virtual element method.

\medskip

\item \textsf{In the numerical section, the authors should compare their results to standard VEM and NCVEM to highlight any benefit their approach has.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
In the revised manuscript, we have provided many numerical experiments to compare our virtual element methods to the standard VEM and NCVEM. We also explain the benefit of the stabilization-free VEMs in the first paragraph in the introduction.

@@

\end{enumerate}

\section{Response to Reviewer 3}
%\smallskip \noindent {\bf Response to Reviewer 2}.

\begin{enumerate}[1.]
\item \textsf{The paper under review presents an interesting and promising idea to avoid the stabilization term in the Virtual Element Method. The procedure adopted is very general and in principle can be used in many different settings. The paper is well written and the proofs are given with appropriate details. 
The only modification I require is a more in-depth comparison with the classical stabilized version with respect to the computational cost, in the two- and three-dimensional case, by making explicit examples in cases of interest.}

\smallskip \noindent \textcolor[rgb]{1.00,0.00,0.00}{Reply.}
In the revised manuscript, we have provided many numerical experiments to compare our virtual element methods to the classical stabilized VEMs in two dimensions. The comparison in three dimensions will be provided in future work.

### 2023-03-12 stabfreevem_sinum.tex
update numerical results

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=5cm]{./figures/convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=5cm]{./figures/nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
$\mathcal T_1$(right).}
\label{fig:mesh}
\end{figure}

\section{Numerical results}\label{sec:numericalexamps}
In this section, we will numerically verify the convergence of the nonconforming virtual element method \eqref{eq:vem} and the conforming
virtual element method \eqref{eq:cfmvem}.
The numerical example is implemented by using the FEALPy package \cite{fealpy}

% \begin{example}\label{ex}
Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 2$
on rectangular domain $\Omega = (0, 1)\times(0, 1)$. 
The exact solution and source term are given by
\[
u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y).
\]
% \end{example}

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Fig.~\ref{fig:rate1}. We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Fig.~\ref{fig:rate2}. Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
of nonconforming virtual element method \eqref{eq:vem} on 
$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate1}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/cvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/cvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0$ 
of conforming virtual element method \eqref{eq:cfmvem} on $\mathcal T_0$(left) and 
$\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate2}
\end{figure}

>>>>

% \begin{figure}[htbp]
% \centering
% \begin{minipage}[t]{0.49\linewidth}
% \centering
% \includegraphics[width=5cm]{./figures/convex.pdf}
% %\caption{Numberical result of example with $\mathcal T_0$.}
% \end{minipage}%
% \begin{minipage}[t]{0.49\linewidth}
% \centering
% \includegraphics[width=5cm]{./figures/nonconvex.pdf}
% %\caption{[Numberical result of example with $\mathcal T_1$].}
% \end{minipage}%
% \centering
% \caption{Convex polygon mesh $\mathcal T_0$(left) and non-convex polygon mesh 
% $\mathcal T_1$(right).}
% \label{fig:mesh}
% \end{figure}

\section{Numerical results}\label{sec:numericalexamps}
In this section, we will numerically test the stabilization-free nonconforming virtual element method \eqref{eq:vem} and the stabilization-free conforming
virtual element method \eqref{eq:cfmvem}, which are abbreviated as SFNCVEM and SFCVEM respectively.
For the convenience of narration, we also abbreviate the standard conforming virtual element
method in \cite{BeiraoBrezziCangianiManziniEtAl2013} and non-conforming virtual element method  in \cite{CangianiManziniSutton2017} as CVEM and NCVEM respectively. 
We implement all the experiments by using the FEALPy package \cite{fealpy} on a PC with AMD Ryzen
5 3500U CPU and 64-bit Ubuntu 22.04 operating system.
Set the rectangular domain $\Omega = (0, 1)\times(0, 1)$.

\subsection{Verification of convergence}
% \begin{example}\label{ex}
Consider the second order elliptic problem \eqref{eq:ellipitc2ndproblem} with $\alpha = 2$.
The exact solution and source term are given by
\[
u = \sin(\pi x)\sin(\pi y), \quad f = (2\pi^2+2)\sin(\pi x)\sin(\pi y).
\]
% \end{example}

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$ in Fig. \ref{fig:mesh}, respectively. 
In both SFNCVEM and SFCVEM, we choose $k = 1, 2, 5$.
The numerical results of the SFNCVEM on meshes $\mathcal T_0$ and $\mathcal T_1$ are shown in Fig.~\ref{fig:rate1}. We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
And the numerical results of the SFCVEM are presented in Fig.~\ref{fig:rate2}. Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
\begin{figure}[htbp]
\subfigure[Convex polygon mesh $\mathcal T_0$.]{
\begin{minipage}[t]{0.425\linewidth}
\centering
\includegraphics*[width=4.7cm]{./figures/convex.pdf}
\end{minipage}}%% 
\quad \quad
\subfigure[Non-convex polygon mesh 
$\mathcal T_1$.]
{\begin{minipage}[t]{0.425\linewidth}
\centering
\includegraphics*[width=4.7cm]{./figures/nonconvex.pdf}
\end{minipage}}
\caption{Convex polygon mesh and non-convex polygon mesh.}
\label{fig:mesh}
\end{figure}
\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=5.5cm]{./figures/ncvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=5.5cm]{./figures/ncvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
of nonconforming virtual element method \eqref{eq:vem} on 
$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate1}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=5.5cm]{./figures/cvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=5.5cm]{./figures/cvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0$ 
of conforming virtual element method \eqref{eq:cfmvem} on $\mathcal T_0$(left) and 
$\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate2}
\end{figure}

\subsection{The invertibility of the local stiffness matrices}

We construct three different hexagons shown in Fig. \ref{fig:hexagon}, and calculate the eigenvalues of local stiffness matrices with $k=3$ for four virtual element methods. Our numerical results show that, on each different hexagon, both SFNCVEM and SFCVEM have only one zero eigenvalue. In Tables \ref{tab:comparison0}-\ref{tab:comparison2}, we also present the minimum non-zero eigenvalue, the maximum eigenvalue and the condition number for the local stiffness matrix on different hexagons in Fig. \ref{fig:hexagon}, by which we can see that these quantities are comparable for four virtual element methods.
% \begin{figure}[htbp]
% \centering
% \subfigure{\includegraphics[width=1.4in]{./figures/hexagon0.pdf}}
%     % \caption{Type I:5 tetrahedra}
% %%
% \subfigure{\includegraphics[width=1.4in]{./figures/hexagon1.pdf}}
%      %\caption{Type II: 24 tetrahedra}
% %%
% \subfigure{\includegraphics[width=1.2in]{./figures/hexagon2.pdf}}
%      %\caption{Trirectangular tetrahedron}
% %%
% \caption{The regular hexagon(Left), the quasi-regular hexagon generated by regular
%     hexagon with a small perturbation (Middle), 
% and the square with two hanging nodes (Right)}
%   \label{fig:hexagon0} %% label for entire figure
% \end{figure}
\begin{figure}[htbp]
\subfigure[Regular hexagon.]{
\begin{minipage}[t]{0.3\linewidth}
\centering
\includegraphics*[width=1in]{./figures/hexagon0.pdf}
\end{minipage}}%% 
\;\;% \quad
\subfigure[Quasi-regular hexagon generated by regular
    hexagon with a small perturbation.]
{\begin{minipage}[t]{0.3\linewidth}
\centering
\includegraphics*[width=1in]{./figures/hexagon1.pdf}
\end{minipage}}
\;\;% \quad
\subfigure[Square with two hanging nodes.]
{\begin{minipage}[t]{0.35\linewidth}
\centering
\includegraphics*[width=0.9in]{./figures/hexagon2.pdf}
\end{minipage}}
\caption{The regular hexagon(Left), the quasi-regular hexagon generated by regular
    hexagon with a small perturbation (Middle), 
and the square with two hanging nodes (Right).}
\label{fig:hexagon}
\end{figure}
\begin{table}[htbp]
\centering
\caption{Comparison of eigenvalues and condition numbers on the regular hexagon.}
\label{tab:comparison0}
\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
\hline
\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
eigenvalue} & \textbf{Condition number} \\ \hline
NCVEM & 975.5693189 & 0.309674737 & 3150.303211 \\ \hline
CVEM & 1012.488116 & 0.297206358 & 3406.683909 \\ \hline
SFNCVEM & 992.5956147 & 0.318932029 & 3112.248147 \\ \hline
SFCVEM & 1011.173331 & 0.298509692 & 3387.405362 \\
\hline
\end{tabular}
\end{table}
\begin{table}[htbp]
\centering
\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
\label{tab:comparison1}
\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
\hline
\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
eigenvalue} & \textbf{Condition number} \\ \hline
NCVEM   & 935.2883848 & 0.279027715 & 3351.955143 \\ \hline
CVEM    & 1014.672395 & 0.257370621 & 3942.456177 \\ \hline
SFNCVEM & 997.4831245 & 0.282126359 & 3535.589964 \\ \hline
SFCVEM  & 1047.876056 & 0.258970708 &
4046.311124 \\
\hline
\end{tabular}
\end{table}
\begin{table}[htbp]
\centering
\caption{Comparison of eigenvalues and condition numbers on the quasi-regular hexagon}
\label{tab:comparison2}
\begin{tabular}{c|p{3cm}<{\centering}p{3.5cm}<{\centering}p{3cm}<{\centering}}
\hline
\textbf{Method} & \textbf{Maximum eigenvalue} & \textbf{Minimum nonzero
eigenvalue} & \textbf{Condition number} \\ \hline
 NCVEM   & 941.8571938&	0.21069027	&4470.340249 \\ \hline
 CVEM    & 1046.755495&	0.200435123	&5222.4155 \\ \hline
 SFNCVEM & 986.5963357&	0.212761106	&4637.108513 \\ \hline
 SFCVEM  & 1061.651989&	0.202074633	&5253.761808 \\
\hline
\end{tabular}
\end{table}

\subsection{Comparison of assembling time}
The only difference between the standard VEMs and the stabilization-free VEMs is the
stiffness matrix, so we compare the time consumed in assembling the stiffness matrix of
four different VEMs in detail by varying the degree $k$ and the mesh size $h$
respectively. We use the mesh in Fig.~\ref{fig:mesh}(a) for this experiment.
The results presented in Tables
\ref{tab:ptime} and \ref{tab:ttime} show that NCVEM, CVEM and SFNCVEM have similar assembling time. 
However, SFCVEM requires more time due to the projection onto the one-order higher polynomial space.
\begin{table}[htbp]
\caption{Time consumed in assembling stiffness matrix of four VEMs with
 $h=0.2$ and different $k$.}
\label{tab:ptime}
\centering
\begin{tabular}{c|cccc}
\hline
$k$ & 2 & 4 & 8 & 10 \\
\hline
SFCVEM & 0.053684235 & 0.144996881 & 1.468627453 & 2.603836536 \\
SFNCVEM & 0.022516727 & 0.065697193 & 0.806378841 & 1.554260015 \\
CVEM & 0.021185875 & 0.059809923 & 0.600241184 & 1.160929918 \\
NCVEM & 0.0213027 & 0.061014891 & 0.596506596 & 1.129639149 \\
\hline
\end{tabular}
\end{table}
\begin{table}[htbp]
\caption{Time consumed in assembling stiffness matrix of four VEMs with $k = 5$ and different $h$.}
\label{tab:ttime}
\centering
\begin{tabular}{c|cccc}
\hline
$h$ &    1	& 0.25 & 0.0625 & 0.03125\\
\hline
SFCVEM & 0.039689541 & 0.199015379	& 1.74412179	& 4.75462532\\
SFNCVEM & 0.018287182 & 0.100006819	& 0.81251812	& 2.465409517\\
CVEM & 0.018686771 & 0.087426662	& 0.781031132	& 1.983617783\\
NCVEM & 0.018309593 & 0.096345425	& 0.767129898	& 2.159288645\\
\hline
\end{tabular}
\end{table}

\subsection{Condition number of the stiffness
matrix}
\begin{figure}[htbp]
\centering
\subfigure{\includegraphics[width=1in]{./figures/hexagon0.pdf}}
    % \caption{Type I:5 tetrahedra}
%%
\subfigure{\includegraphics[width=1in]{./figures/hexagon3.pdf}}
     %\caption{Type II: 24 tetrahedra}
%%
\subfigure{\includegraphics[width=1in]{./figures/hexagon4.pdf}}
     %\caption{Trirectangular tetrahedron}
%%
\caption{The hexagons $H_0, H_1, H_2$.}
  \label{fig:collapsehexagon} %% label for entire figure
\end{figure} 
We design two experiments to check the condition number of the stiffness
matrices of the four VEMs.

Firstly, we refer to the ``collapsing polygons'' experiment in
\cite{Mascotto2018} and consider a sequence of hexagons
$\{H_i\}_{i=0}^{\infty}$, where the vertices of $H_i$ are given by
$A_i = (1, 0)$, $B_i = (0.5, a_i)$, $C_i = (-0.5, a)$, $D_i=(-1, 0)$, 
$E_i = (-0.5, -a_i)$, and $F_i = (0.5, -a_i)$,
where $a_i = \frac{\sqrt{3}}{2^{i+1}}$. The hexagons $H_0$, $H_1$ and $H_2$ are drawn
in Fig.~\ref{fig:collapsehexagon}. 
% We construct the virtual element space on $H_i$ and calculate the condition number
% of the stiffness matrix of four methods. 
As shown in Fig.~\ref{fig:collapsehexagon_conditionnumber}, the condition numbers of stiffness
matrices of the stabilization-free methods are smaller than those of the standard methods when $i$ is large.

\begin{figure}[htbp]
\subfigure[$k = 8$]{
\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics*[width=2in]{./figures/collapsing_condition_number_8.pdf}
\end{minipage}}%% 
\quad \quad
\subfigure[$k = 10$]
{\begin{minipage}[t]{0.45\linewidth}
\centering
\includegraphics*[width=2in]{./figures/collapsing_condition_number_10.pdf}
\end{minipage}}
\caption{The condition number of stiffness matrix of four VEMs on
$\{H_i\}_{i=0}^{12}$.}
\label{fig:collapsehexagon_conditionnumber}
\end{figure}

% \begin{figure}[htbp]
% \centering
% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_8.pdf}}
% \subfigure{\includegraphics[width=2.2in]{./figures/collapsing_condition_number_10.pdf}}
% \caption{The condition number of stiffness matrix of four VEMs on
% $\{H_i\}_{i=0}^{12}$, Left : $k = 8$, Right : $k = 10$.}
%   \label{fig:collapsehexagon_conditionnumber0} %% label for entire figure
% \end{figure}
